\documentclass[a4paper,11pt,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{black}    % black, blue, burgundy, green
\moderncvhead{1}  % 1, 3, 6
\moderncvicons{awesome}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{3cm} % grow the width of the column with the dates

\name{Fotis}{Xenakis}
\title{Software Engineer, Systems}
\email{foxen@windowslive.com}
\social[linkedin]{fotis-xenakis}
\social[github]{foxeng}
\born{12 Jan 1996}


\begin{document}

\makecvtitle

\section{Experience}
\cventry{01/2024 - now}{Kernel / Hypervisor Engineer}{\httpslink[AWS]{www.aws.amazon.com}}{Berlin, Germany}{}{
    EC2 Accelerated Nitro
    \newline
    Working on the accelerated platforms of EC2, ranging from the depths of the
    EC2 Nitro hypervisor up to effective fleet management for the flagship EC2
    platforms powering ML workloads.
}
\cventry{06/2023 - 11/2023}{Senior Software Engineer, Systems}{\httpslink[Mobileum]{www.mobileum.com}}{Athens, Greece}{}{}
\cventry{10/2021 - 05/2023}{Software Engineer, Systems}{\httpslink[Mobileum]{www.mobileum.com}}{Athens, Greece}{}{
    Engagement \& Experience Business Unit (ex-\httpslink[Niometrics]{www.mobileum.com/about/news-press-releases/mobileum-acquires-niometrics/})
    \newline
    Working on the Deep Network Analytics platform, doing high-performance
    (GB/s), highly parallel log indexing, storage and aggregation. Heavily
    performance-focused: development, observability, troubleshooting in large
    production deployments. Involved in the entire development lifecycle
    (requirements, design, implementation, testing, support), member of a highly
    distributed team.
    C, Linux.
}
\cventry{11/2020 - 10/2021}{Military service}{Hellenic Navy}{}{}{}
\cventry{05/2019 - 10/2020}{Software Engineer}{\httpslink[Programize]{www.programize.com}}{Athens, Greece}{}{
    Working with Silicon Valley startups.
    \begin{itemize}
        \item \httpslink[Aporeto/Palo Alto Networks]{www.paloaltonetworks.com/company/press/2019/palo-alto-networks-completes-acquisition-of-aporeto}:
              Scale testing and benchmarking of a cloud-native distributed
              firewall and network monitoring solution.
              Linux, Docker, Kubernetes, Go, Ansible, Terraform, Bash, GCP.
        \item \httpslink[Codex]{www.codex.health}: Back-end development and
              DevOps for a modern platform aimed at healthcare providers.
              Python, Django, GCP.
    \end{itemize}
}
\cventry{07/2018 - 11/2023}{System Administrator (part-time)}{PCLab, \httpslink[ECE NTUA]{www.ece.ntua.gr/}}{Athens, Greece}{}{
    GNU/Linux deployment and administration of a 128-PC lab for the school's
    students. Implementation of a
    \httpslink[mechanism]{github.com/foxeng/PCLab-Arch} for automated file
    system resets upon user login. Linux, Ansible, Bash.
}
\cventry{01/2020 - 12/2020}{Contributor}{\httpslink[OSv]{github.com/cloudius-systems/osv}}{}{}{
    Mainly around \httpslink[virtio-fs]{virtio-fs.gitlab.io}. C++, QEMU/KVM.
}

\section{Education}
\cventry{2014 - 2020}{Diploma Electrical and Computer Engineering}{\httpslink[National Technical University of Athens]{www.ntua.gr/}}{}{\textit{8.58/10}}{
    Major: computer software, computing systems. Minor: networking, mathematics.
    \newline
    \httpslink[Thesis]{github.com/foxeng/diploma} title: \textit{Efficient
    file sharing between host and unikernel.}
}
\cventry{2002 - 2014}{High School Degree}{\httpslink[Experimental School of the University of Athens]{pspa.eu}}{}{}{}

\section{Conferences}
\cvitem{\httpslink[HiPEAC 2020]{www.hipeac.net/2020/bologna}}{Attended.}
\cvitem{\httpslink[HiPEAC CSW Autumn 2019]{www.hipeac.net/csw/2019/bilbao}}{
    Attended and qualified in the
    \httpslink[Student Challenge]{www.hipeac.net/news/6905/hipeac-student-challenge-vii-the-tables-are-turned-again},
    proposing an open, modular and affordable approach to home automation.
}

\section{Languages}
\cvitemwithcomment{Greek}{Native}{}
\cvitemwithcomment{English}{C2 (proficient)}{Certificate of Proficiency in English, The University of Michigan}
\cvitemwithcomment{German}{A2 (basic)}{A2}
\cvitemwithcomment{French}{A2 (basic)}{DELF A2}

\pagebreak

\section{Areas of interest}
\cvitem{}{Operating Systems, Storage Systems, Performance, Programming Languages, Virtualization}

\section{Technical skills}
\cvdoubleitem{Programming:}{
    \begin{itemize}
        \item Solid: C, C++, Python, Go, Shell
        \item Familiar: Java, Rust
    \end{itemize}
}{}{}
\cvdoubleitem{Version control:}{Git}{Virtualization:}{QEMU, KVM}
\cvdoubleitem{Operating systems:}{Linux}{Cloud computing:}{GCP, AWS, Terraform}
\cvdoubleitem{Web development:}{Django, Flask}{Other:}{Docker, Kubernetes, Ansible}

\end{document}
